---
title: "Edinburgh Airbnb Anaysis"
subtitle: "Due: 11 February, 17:48 TR time"
output: 
  tufte::tufte_html:
    css: ../hw.css
    tufte_variant: "envisioned"
    highlight: pygments
link-citations: yes
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(ggplot2)
    
knitr::opts_chunk$set(out.width = "100%")
```

**Note: Since I do not have the photo, it gives an error while knit. That's why I removed the photo.**



## Some Information About Packages

This assignment will use the following packages:

-   `tidyverse`: a collection of packages for doing data analysis in a "tidy" way
-   `ggplot2`: a package that contains the function for the grammer of graphics
-   `lubridate`: a package for formatting dates in R (in case if you need)

We use the `library()` function to load packages.
In your R Markdown document you should see an R chunk labelled `load-packages` which has the necessary code for loading both packages.

```{r load-packages}
library(tidyverse)
library(ggplot2)
library(lubridate)
```


# Airbnb Listings in Edinburgh

Airbnb is an online marketplace where people can book short-term stays in hotels or in other people's houses.
Recent developments in Edinburgh regarding the growth of Airbnb and its impact on the housing market means a better understanding of the Airbnb listings is needed.
Using data provided by Airbnb, we can explore how Airbnb availability and prices vary by neighbourhood.

## Column Descriptors

The `edibnb` data set contain `r nrow(edibnb)` listings in Edinburgh, with values about `r ncol(edibnb)` different variables that includes the property neighborhood location, number of rooms and review ratings.

Edinburgh council collects the second data set from their assessments of a randomly selected sample of listings.

The variables in this data set are: 
- `id`, the ID number of the listing (according to `edibnb`) 
- `price`, the daily rate of the accommodation unit
- `neighborhood`, indicates in which neighbourhood the accommodation is located
- `accommodates`, indicates how many people the accommodation can accommodate
- `bathrooms`, indicates how many bathrooms the accommodation unit
- `bedrooms`, indicates how many bedrooms are in the accommodation unit
- `beds`, indicates how many beds are in the accommodation unit
- `review_scores_rating`, the council's rating of the listing of the property either being good, adequate or poor.
- `number of reviews`, indicates how many of the people who have stayed here before have made a review
- `listing url`, the url of the accommodation

------------------------------------------------------------------------

```{r load-edibnb-data, message = FALSE}
edibnb <- read_csv("C:/Projects/0_Github/Edinburgh_Airbnb_Analysis/edibnb.csv")
```

------------------------------------------------------------------------

We can view the dataset as a spreadsheet using the `View()` function.

```{r view-data, eval = FALSE}
View(edibnb)
```

The data is contained in the file `council_assessments.csv`

```{r message = FALSE}
council <- read_csv("C:/Projects/0_Github/Edinburgh_Airbnb_Analysis/council_assessments.csv")
```

## Exercise 1 (15 pts)

-   In the `edibnb` data set, what is the ID of the listing that has the highest number of reviews with a perfect review score of 100%?

-   Which variables have the missing observations in the `edibnb` data set.

-   Visualize the missing observations using some functions from visdat or naniar packages

```{r, Question1}

#Task 1
rev_scores <- subset(edibnb, review_scores_rating == 100)
max_reviews <- max(rev_scores$number_of_reviews)
id_max_reviews <- rev_scores$id[rev_scores$number_of_reviews == max_reviews]

#Task 2
library(visdat)
vis_miss(edibnb)

#Task 3
library(naniar)
gg_miss_var(edibnb)
```


*Task1*
Firstly, I created the cells equal to 100 in the review_scores_rating column in the dataset as a subset to rev_scores. Then I used the max function to find the one with the most reviews among them and threw it into max_reviews. Here I found the value 612. 612 indicated the review value and I needed the id of this value. For this reason, I found the id by querying the max_reviews(612) value that matches the number_of_reviews value in rev_scores. ID 860170 came out. In other words, I found that the id with 860170 has the most reviews among the accommodation with the most ratings. 

*Task2*
I want to know how much NA is in the values in the dataset. The vis_miss function in the visdat library is used to visualise the NA values. 

*Task3*
I visualised missing variables with the gg_miss_var function in the naniar library

